---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# genomeverse

<!-- badges: start -->
<!-- badges: end -->

genomeverse is a collection of R packages that are designed to work together seamlessly to create reproducible clinico-genomic analysis pipelines

## Installation

You can install the development version of genomeverse from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MSKCC-Epi-Bio/genomeverse")
```

## Usage

`library(genomeverse)` will load the core genomeverse packages: 

* [cbioportalR](https://www.karissawhiting.com/cbioportalR/), for pulling data from cBioPortal.
* [oncokbR](https://tidyr.tidyverse.org), for oncoKB annotation fo data.
* [gnomeR](https://mskcc-epi-bio.github.io/gnomeR/), for processing raw mutation, CNA and fusion files.

You also get a condensed summary of conflicts with other packages you have loaded:

```{r example}
library(genomeverse)
```

## Code of Conduct

Please note that the tidyverse project is released with a [Contributor Code of Conduct](https://tidyverse.tidyverse.org/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
